Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 b

### 2018-04-28 ms.tex
KS tests and better comparison histogram.

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/amp_distributions_comparison.pdf}
\caption{Distributions from 2 photometric campaigns and the Kepler data.}\label{fig:histoPhot}
\end{centering}
\end{figure*}

>>>>

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/amp_distributions_comparison.pdf}
\caption{Normalized frequency of 3 different distributions: 1) all of the Kepler Long Cadence data from 2009 to 2013, 2) the 8 night ground-based IRTF campaign in the summers of 2013 and 2014 from \citet{schlawin2016kic1255} (S16) and 3) the 5 night Kuiper observatory campaign in the summer of 2016.
The \citet{schlawin2016kic1255} (S16) evens give a Kolmogorov Smirnov p value of 0.001 of the null hypothesis that the S16 results are drawn from the same distribution as the Kepler Long Cadence.
In contrast, the 2016 photometric results in this work are consistent with the Kepler Long Cadence data, giving a  p value of 0.5 of the null hypothesis.}\label{fig:histoPhot}
\end{centering}
\end{figure*}
